Relating two Abstractions for Formal Array Languages

### 2014-04-14 paper.tex
I found a few more typos
Nothing important but I found two more typos when I read it again.

Shapes in Pull arrays are represented by a completely different type,
whereas in MoA shapes are simply arrays. Representing shapes as arrays
is challenging in a typed language such as Haskell because it leads to
a form of infinite recursion and while there are a number of way to
break the recursion we have yet to find a way that does so and retains
the efficiency and simplicity of Pull arrays.

>>>>

Shapes in Pull arrays are represented by a completely different type,
whereas in MoA shapes are simply arrays. Representing shapes as arrays
is challenging in a typed language such as Haskell because it leads to
a form of infinite recursion and while there are a number of ways to
break the recursion we have yet to find a way that does so and retains
the efficiency and simplicity of Pull arrays.
